---
title: "SydneyEnergyResearch"
subtitle: "Electricity"
author: "© University of Sydney 2023"
date: 30/03/2023
output:
  html_document:
    fig_caption: yes
    number_sections: yes
    self_contained: yes
    theme: flatly
    css: 
      - https://use.fontawesome.com/releases/v5.0.6/css/all.css
    toc: true
    toc_depth: 3
    toc_float: true
    code_folding: hide
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r include=FALSE}
library(readxl)
data2019 <- read_excel("data/Ausgrid average electricity consumption by LGA 201819.xlsx", range = "A1:Q40")
data2020 <- read_excel("data/Ausgrid average electricity consumption by LGA 2020.xlsx", range = "A2:Q43")
data2023 <- read_excel("data/Ausgrid average electricity consumption by LGA 202223 excel.xlsx", range = "A2:Q43")
```
Taking a quick view of the data
```{r eval=TRUE}
# For the 2019 data set
dim(data2019)
head(data2019, 10)
# For the 2020 data set
dim(data2020)
head(data2020, 10)
# For the 2023 data set
dim(data2023)
head(data2023, 10)
```
## Data source verification
This data source is from Ausgrid, which is a large electricity provider that has more than 1.7 million customers in Sydney, Australia.Although this is a electricty provider that is run by a company, however, it must be subjected to a range of regulations and guidelines to ensure the accuracy of their data, including the Australian Energy Regulator(AER), according to the Australian energy policies.

Some useful functions
```{r}
filter_int <- function(data){
  integers <- as.numeric(grep("\\d+", data, value = TRUE))
  max_index <- which(integers == max(integers))
  return(integers[-max_index])
}
ex_cwords <- function(words) {
  capital_words <- words[str_detect(words, "^([A-Z]+)$")]
  return(capital_words)
}
wrap.it <- function(x, len)
{ 
  sapply(x, function(y) paste(strwrap(y, len), 
                              collapse = "\n"), 
         USE.NAMES = FALSE)
}

wrap.labels <- function(x, len)
{
  if (is.list(x))
  {
    lapply(x, wrap.it, len)
  } else {
    wrap.it(x, len)
  }
}
```
## Research question 1:
The impact of the covid-19 pandemic on electricity consumption in the different suburbs of Sydney
As covid-19 strikes Australia, our reliance on digital equipments especially remote streaming apps has increased drastically.So, the hypothesis is the usage of digital equipments has led to a increase in electricity consumption.
Is there an electricity usage rise during the pandemic?

## IDA
To get an idea of the new data, we will do a quick bargraph of the 'general supply' columns from the excel file.
(It is with several trial and error, that we have found out the original excel file is not suitable for R data analysis, therefore manual excel operation was done to extract it out into a form which was useful.)
```{r eval=TRUE}
library(readxl)
library(dplyr)
options(scipen = 999)

# Read in files
extracted_data <- read_excel("data/Electricity_consumption(extracted).xlsx")
extracted_data <- arrange(extracted_data)

# Setting up the output graph
par(mar = c(5, 8, 0, 2), mgp = c(4, 1, 0))

# The 2019 Dataset
values2019 <- extracted_data$`2019-R`
suburbs2019 <- extracted_data$H2019
barplot(values2019, names.arg=wrap.labels(rev(suburbs2019), 20), 
        col="red", xlab=" Electricity consumption/MWh", horiz=T, las=2, cex.names = 0.7)

# The 2020 Dataset
values2020 <- extracted_data$`2020-R`
suburbs2020 <- extracted_data$H2020
barplot(values2020, names.arg=wrap.labels(rev(suburbs2020), 20), 
        col="green", xlab=" Electricity consumption/MWh", horiz=T, las=2, cex.names = 0.7)

# The 2021 Dataset
values2021 <- extracted_data$`2021-R`
suburbs2021 <- extracted_data$H2021
barplot(values2021, names.arg=wrap.labels(rev(suburbs2021), 20), 
        col="blue", xlab=" Electricity consumption/MWh", horiz=T, las=2, cex.names = 0.7)
```
It seems like the data itself is not distinctive enough to be able figure out the difference from first site.

```{r eval=TRUE}
sdev1 = mean(values2019)
sdev2 = mean(values2020)
sdev3 = mean(values2021)
ts = c(sdev1, sdev2, sdev3)
barplot(ts, names.arg=c('2019', '2020', '2021'))
```
It seems like the hypothesis has been falsified, there was a slight electric usage increase, but not during pandemic, instead it was after the pandemic in 2021
To investigate further why this is the case, we can add the 2022 dataset into the mix.
(Note: Some datas from 2022 is missing, it's supposed to be updated to record the 2023 dataset later)
```{r}
values2022 <- extracted_data$`2022-R`
values2022 <- na.omit(values2022)
sdev4 <- mean(values2022)
cp <- c(sdev1, sdev2, sdev3, sdev4)
barplot(cp, names.arg=c('2019', '2020', '2021', '2022-2023'))
print(sdev4-sdev2)
```
So, the first hypothesis has failed, after some more research it has found that the reason why there was an increase of electric usage from 2021 to 2022 is a complicated matter.It's mainly caused by the fact that the energy policies are switching to one that is more suitable for wider applications of renewable energies in the power grid.
However, it is also considered that as some values from the 2022-2023 dataset is missing, part of this could also contributed to this phenomenon.

## Research question 2:
It logically makes sense that the city areas uses the most amount of electricity, since the population density in the city is much higher than other areas.

(We'll use the latest complete dataset, which was the 2021 dataset, with the general supply column)
```{r eval=TRUE}
distribution <- function(title, name, values){
  df <- data.frame(label=name, value=values)
  df_sorted <- df[order(df$value, decreasing = FALSE),]
  mean_val <- mean(values)
  sd_val <- sd(values)
  par(mar = c(5, 6, 2, 2), mgp = c(4, 1, 0), fig = c(0, 1, 0, 1), fin = c(6, 4))
  barplot(df_sorted$value, names.arg=wrap.labels(df_sorted$label, 20), 
        col="blue", xlab=title, horiz=T, las=2, cex.names = 0.4, , cex.lab=0.7, cex.axis=0.7)
  hist(values, breaks=10, freq=FALSE, col="grey", xlab="Values", main="Normal Distribution")
  curve(dnorm(x, mean=mean_val, sd=sd_val), add=TRUE, col="blue")
  abline(v = mean_val, col = "red", lwd = 2)
}
distribution("Electricity Consumption/MWh", suburbs2021, values2021)
```
As can see, the electricity consumption of general supplies is actually skewed towards the lower end, which meant that the majority of the suburbs don't actually uses as much compared to few areas which uses really high amounts of electricity.
To see why, we can switch the target column from 'General Supply' to 'Non residential large sites' which usually spend 160 megawatts per hour
```{r eval=TRUE}
values2021L <- extracted_data$`2021-L`
distribution("Electricity Consumption/MWh",suburbs2021, values2021L)
```
'Non residential medium sites'
```{r eval=TRUE}
values2021M <- extracted_data$`2021-M`
distribution("Electricity Consumption/MWh",suburbs2021, values2021M)
```
As can see, this shows a nuanced side of the distribution of electricity consumption by Ausgrid, as Ausgrid is the largest distributor of electricity on the east coast, it can be considered as reflective of the total electricity consumption of Sydney.The majority of electricity spent is by the city areas, but depending on what your target customer is.
(Note: It is considered )
Finally, to make a conclusion, a pie chart is made
```{r eval=TRUE}
par(mar = c(5, 6, 2, 2), mgp = c(4, 1, 0), fig = c(0, 1, 0, 1), fin = c(6, 4))
sum_2021G <- sum(values2021)
sum_2021M <- sum(values2021M)
sum_2021L <- sum(values2021L)
pie_values <- c(sum_2021G, sum_2021M, sum_2021L)
pie_labels <- c("General Supply", "Medium Sites", "Large Sites")
pie(pie_values, labels = pie_labels)
```

As can see, depending on what kind of electricity consumption you're looking at, the differences between urban areas and suburban areas varies.
However, the question in mind was more about residential areas.
```{r eval=TRUE}

```