---
title: "SydneyEnergyResearch"
subtitle: "Electricity"
author: "© University of Sydney 2023"
date: 
output:
  html_document:
    fig_caption: yes
    number_sections: yes
    self_contained: yes
    theme: flatly
    css: 
      - https://use.fontawesome.com/releases/v5.0.6/css/all.css
    toc: true
    toc_depth: 3
    toc_float: true
    code_folding: hide
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Data Story
The impact of the covid-19 pandemic on electricity consumption in the different suburbs of Sydney
As covid-19 strikes Australia, our reliance on digital equipments especially remote streaming apps has increased drastically.So, the hypothesis is the usage of digital equipments has led to a increase in electricity consumption.

```{r include=FALSE}
library(readxl)
data2019 <- read_excel("data/Ausgrid average electricity consumption by LGA 201819.xlsx", range = "A1:Q40")
data2020 <- read_excel("data/Ausgrid average electricity consumption by LGA 2020.xlsx", range = "A2:Q43")
data2023 <- read_excel("data/Ausgrid average electricity consumption by LGA 202223 excel.xlsx", range = "A2:Q43")
```
Taking a quick view of the data
```{r eval=TRUE}
# For the 2019 data set
dim(data2019)
head(data2019, 10)
# For the 2020 data set
dim(data2020)
head(data2020, 10)
# For the 2023 data set
dim(data2023)
head(data2023, 10)
```
Some useful functions
```{r}
filter_int <- function(data){
  integers <- as.numeric(grep("\\d+", data, value = TRUE))
  max_index <- which(integers == max(integers))
  return(integers[-max_index])
}
ex_cwords <- function(words) {
  capital_words <- words[str_detect(words, "^([A-Z]+)$")]
  return(capital_words)
}
wrap.it <- function(x, len)
{ 
  sapply(x, function(y) paste(strwrap(y, len), 
                              collapse = "\n"), 
         USE.NAMES = FALSE)
}

wrap.labels <- function(x, len)
{
  if (is.list(x))
  {
    lapply(x, wrap.it, len)
  } else {
    wrap.it(x, len)
  }
}
```
## IDA
To get an idea of the new data, we will do a quick bargraph of the 'general supply' columns from the excel file.
(It is with several trial and error, that we have found out the original excel file is not suitable for R data analysis, therefore manual excel operation was done to extract it out into a form which was useful.)
```{r eval=TRUE}
library(readxl)
library(dplyr)
options(scipen = 999)
extracted_data <- read_excel("data/Electricity_consumption(extracted).xlsx")
extracted_data <- arrange(extracted_data)

# Setting up the output graph
par(mar = c(5, 8, 0, 2), mgp = c(4, 1, 0))

# The 2019 Dataset(From general supply)
values2019 <- extracted_data$`2019-R`
suburbs2019 <- extracted_data$H2019
barplot(values2019, names.arg=wrap.labels(rev(suburbs2019), 20), 
        col="red", xlab=" Electricity consumption/mgh", horiz=T, las=2, cex.names = 0.7)

# The 2020 Dataset
values2020 <- extracted_data$`2020-R`
suburbs2020 <- extracted_data$H2020
barplot(values2020, names.arg=wrap.labels(rev(suburbs2020), 20), 
        col="green", xlab=" Electricity consumption/mgh", horiz=T, las=2, cex.names = 0.7)

# The 2023 Dataset
values2023 <- na.omit(extracted_data$`2023-R`)
suburbs2023 <- na.omit(extracted_data$`H-2023`)
barplot(values2023[1:14], names.arg=wrap.labels(rev(suburbs2023), 20), 
        col="blue", xlab=" Electricity consumption/mgh", horiz=T, las=2, cex.names = 0.7)
```
Remark 1: (There's some value in the third dataset that is missing, which meant that the totals from each year is not investigated, as that would yield misconceptions)
